Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
Rough and meta related work done.

\subsection{Privacy for Smartphones and Wearables}
(REDO) Mention Adrienne's work here, and other cool smartphone studies of any sort. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.

Mention any other privacy studies for wearables (like the ones you can find at Ubicomp, CHI, or SOUPS), and give them a nod. Also highlight how my study is different from previous studies.

>>>>

\subsection{Concerns for Smartphones and Wearables}
(REDO) Mention Adrienne's work here, and other relevant smartphone studies of any sort. I will talk about how I model Adrienne's work in the next section, Survey, just give a nod to it here and go into it later. Since my results were that people care about privacy, security, health, and social change/social stigma, any phone studies which hint at any of those things will be good to put here. Be sure to go cite a fair number of them. Related work section is the part where it looks like I know stuff.

Mention any studies for wearables (like the ones you can find at Ubicomp, CHI, or SOUPS), and give them a nod. Especially mention ones on privacy and perceptions, since I know those exist. I doubt there will be ones for social norm shifts/social stigma, or health concerns, but maybe I can at least include some security ones here too. Throughout mentioning all of these works, highlight how my study is different from previous studies.
